Vegetation Change Assessment - SOD Plots in Sonoma County

### 2016-03-22 veg-change-assessment.Rmd
Add plot of subset of species only in oak plots.

ggplot(os_dbh_in_plot %>%
             filter(species == "umca" | species == "quag" | species == "quga" | species == "psme" | species == "arme" | species == "quke" | species == "quch" | species == "sese") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(tot_ba_m2 = round(sum(tot_ba_m2), 2)), 
       aes(species, tot_ba_m2, label = tot_ba_m2)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year, scales = "free") +
      ylab("basal area") +
      ggtitle("Overstory Species Basal Area") +
      geom_text(aes(vjust = 0), nudge_y = 1.5) +
      theme_bw()

>>>>

ggplot(os_dbh_in_plot %>%
             filter(species == "quag" | species == "quke" | species == "quga" | species == "umca" | species == "psme" | species == "arme" |  species == "quch" | species == "sese") %>% 
             group_by(year, species, stem_status) %>% 
             summarise(tot_ba_m2 = round(sum(tot_ba_m2), 2)), 
       aes(species, tot_ba_m2, label = tot_ba_m2)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ year, scales = "free") +
      ylab("basal area") +
      ggtitle("Overstory Species Basal Area") +
      geom_text(aes(vjust = 0), nudge_y = 1) +
      theme_bw()

qu_plot <- na.omit(left_join(select(oak_sod, plotid, sample_year),
                     os_dbh_in_plot, 
                     by = c("plotid","sample_year"="year")))
summary(qu_plot)

ggplot(qu_plot %>%
             filter(species == "quag" | species == "quke" | species == "quga" | species == "umca" | species == "psme" | species == "arme" |  species == "quch") %>% 
             group_by(sample_year, species, stem_status) %>% 
             summarise(tot_ba_m2 = round(sum(tot_ba_m2), 2)), 
       aes(species, tot_ba_m2, label = tot_ba_m2)) +
      geom_bar(stat = "identity") +
      facet_grid(stem_status ~ sample_year, scales = "free") +
      ylab("basal area") +
      ggtitle("Overstory Species Basal Area in Quercus Plots") +
      geom_text(aes(vjust = 0), nudge_y = 1) +
      theme_bw()
